Results

### 2022-07-07 docs/06_results.Rmd
Figures for presentationns

	# cubic terms ----
	"b_Itime_bin_centerE3:trial_typecognate_noncognate:lpLPMonvs.Bil" = 
		"Trial type (C vs. NC) \u00d7 Group",

@@

@@

@@

	"b_Itime_bin_centerE3" = 
		"Main effect",

	# quadratic terms ----
	"b_Itime_bin_centerE2:trial_typecognate_noncognate:lpLPMonvs.Bil" = 
		"Trial type (C vs. NC) \u00d7 Group",

@@

@@

@@

	"b_Itime_bin_centerE2" = 
		"Main effect",

	# linear terms ----
	"b_time_bin_center:trial_typecognate_noncognate:lpLPMonvs.Bil" = 
		"Trial type (C vs. NC) \u00d7 Group",

@@

@@

@@

	"b_time_bin_center" = 
		"Main effect",

	# marginal terms ----
	"b_trial_typecognate_noncognate:lpLPMonvs.Bil" = 
		"Trial type (C vs. NC) \u00d7 Group",

@@

@@

@@

	# sigma
	"sigma" = "Sigma"
)

draws <- gather_draws(fit_2, `b_.*`, `sigma`, regex = TRUE) %>% 
	mutate(
		.value = ifelse(.variable=="sigma", inv_logit(.value), .value),
		.variable_name = str_replace_all(.variable, str_repl),
		type = case_when(
			str_detect(.variable, "E2") ~ "Quadratic time",
			str_detect(.variable, "E3") ~ "Cubic time",
			str_detect(.variable, "time_bin") ~ "Linear time",
			str_detect(.variable, "sigma") ~ "Error",
			TRUE ~ "Main effects"
		) %>% 
			factor(levels = c("Main effects", "Linear time", "Quadratic time", "Cubic time", "Error"), ordered = TRUE)
	)

draws %>% 
	group_by(.variable, .variable_name, type) %>% 
	mean_qi() %>% 
	select(type, .variable_name, .value, .lower, .upper) %>% 
	gt(rowname_col = ".variable", groupname_col = "type")  %>% 
	fmt_percent(3) %>%
	fmt_number(4:5, scale_by = 100) %>% 
	cols_merge(c(".lower", ".upper"), pattern = "[{1}, {2}]") %>% 
	cols_label(
		.variable_name = md("**Predictor**"),
		.value = md("**Mean**"),
		.lower = md("**95% CrI**")
	) %>% 
	tab_style(
		cell_text(weight = "bold", style = "italic"),
		cells_row_groups()
	) 
as_raw_html()
```

```{r main_effects_plot, echo=FALSE, message=FALSE, warning=FALSE, fig.height=10, fig.width=10}

draws %>% 
	filter(str_detect(.variable, "Intercept")) %>% 
	ggplot(aes(.value, .variable_name)) +
	geom_vline(xintercept = 0.5, colour = "black", linetype = "dashed") +
	stat_pointinterval() +
	labs(
		x = "Value", 
		y = "Variable", 
		fill = "CrI", 
		title = "Intercept",
		alpha = "CrI"
	) +
	guides(fill = "none", color = "none") +
	scale_fill_brewer(direction = -1, na.translate = FALSE) +
	scale_x_continuous(labels = percent, limits = c(0, 1)) +
	theme(
		axis.title.y = element_blank()
	)

draws %>% 
	filter(
		str_detect(
			.variable, 
			"sigma|sd|time_bin", 
			negate = TRUE
		)
	) %>% 
	ggplot() +
	aes(
		x = .value, 
		y = .variable_name,
		colour = .variable_name
	) +
	geom_vline(
		xintercept = 0,
		colour = "black", 
		linetype = "dashed"
	) +
	stat_pointinterval() +
	labs(
		x = "Value", 
		y = "Variable", 
		fill = "CrI", 
		alpha = "CrI",
		title = "Main effects"
	) +
	guides(
		fill = "none", 
		color = "none"
	) +
	scale_color_d3() +
	scale_x_continuous(
		labels = percent,
		limits = c(-0.45, 1)
	) +
	theme(
		axis.title.y = element_blank()
	)

```{r main_effects_plot_time, echo=FALSE, message=FALSE, warning=FALSE, fig.height=10, fig.width=10}

draws %>%
	filter(str_detect(.variable, "time_bin")) %>% 
	mutate(
		.variable_name = factor(
			.variable_name,
			levels = c(
				"Main effect",
				"Group (ML vs. BL)",
				"Trial type (U vs. C+NC)",
				"Trial type (C vs. NC)",
				"Trial type (U vs. C+NC) \u00d7 Group",
				"Trial type (C vs. NC) \u00d7 Group"
			)
		)
	) %>% 
	ggplot() +
	aes(
		x = .value, 
		y = fct_rev(.variable_name),
		colour = type
	) +
	facet_wrap(
		~type, 
		scales = "free_x"
	) +
	geom_vline(
		xintercept = 0,
		colour = "black",
		linetype = "dashed"
	) +
	stat_pointinterval(
		point_size = 1.5
	) +
	labs(
		x = "Value", 
		y = "Variable", 
		fill = "CrI", 
		alpha = "CrI",
		title = "Polynomial effects"
	) +
	scale_color_d3() +
	guides(fill = "none", color = "none") +
	scale_x_continuous(labels = ~percent(., accuracy = 0.1)) +
	theme(
		axis.title.y = element_blank(),
		axis.text.y = element_text(hjust = 1),
		panel.border = element_rect(fill = NA, colour = "grey", size = 0.75),
		panel.grid.major.x = element_line(colour = "grey", linetype = "dotted")
	)

ggsave(here("img", "results_polynomial_terms.png"))
```

```{r main_effects_plot_sigma, echo=FALSE, message=FALSE, warning=FALSE, fig.height=10, fig.width=10}

draws %>% 
	filter(str_detect(.variable, "sigma")) %>% 
	ggplot(
		aes(.value, 
			.variable_name
		)
	) +
	stat_pointinterval() +
	labs(
		x = "Value", 
		y = "Variable", 
		alpha = "CrI",
		fill = "CrI", 
		title = "Error"
	) +
	guides(fill = "none", color = "none") +
	scale_x_continuous(labels = percent, limits = c(0.7, 0.72)) +
	theme(
		axis.title.y = element_blank()
	)

## Random effects

```{r random_effects_participant, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=8, fig.height=4}

corr_mat <- VarCorr(fit_3, summary = TRUE)$participant$cor 
corr_names <- rownames(VarCorr(fit_3, summary = TRUE)$participant$cor)

corr_mat <- corr_mat %>% 
	as_tibble() %>% 
	select(matches("Estimate")) %>% 
	rename_all(str_remove, "Estimate.") %>% 
	mutate(term1 = corr_names)

corr_mat[lower.tri(corr_mat)] <- NA

corr_data <- corr_mat %>% 
	as.data.frame() %>% 
	pivot_longer(
		-term1, 
		names_to = "term2",
		values_to = ".value"
	) %>% 
	drop_na(.value)

corr_data %>% 
	mutate_at(vars(term1, term2), ~paste0("b_", .)) %>% 
	mutate_at(vars(term1, term2), str_replace_all, str_repl) %>% 
	mutate(
		.value_label = case_when(term1==term2 ~ NA_character_, TRUE ~ printnum(.value, gt1 = FALSE)),
		.value = case_when(term1==term2 ~ NA_real_, TRUE ~ .value)
	) %>% 
	filter(term1 != "PTHN × Levenshtein", term2 != "Intercept") %>% 
	ggplot(aes(fct_inorder(term1), fct_rev(fct_inorder(term2)), fill = .value)) +
	geom_tile(na.rm = TRUE) +
	geom_text(aes(label = .value_label), size = 3, na.rm = TRUE) +
	labs(
		x = "Term 1", 
		y = "Term 2", 
		fill = "Posterior\ncorrelation",
		title = "By participant"
	) +
	scale_fill_gradient2(
		low = "#04bf78", mid = "white", high = "#FFC20A", 
		na.value = "white", limits = c(-0.4, 0.4)
	) +
	scale_x_discrete() +
	coord_equal() +
	theme(
		panel.grid = element_blank(),
		legend.position = "top",
		legend.direction = "horizontal",
		legend.key.height = unit(0.1, "cm"),
		legend.key.width = unit(0.3, "cm"),
		legend.justification = c(1, 1),
		legend.title = element_blank(),
		legend.text = element_text(size = 5),
		axis.title.x = element_blank(),
		axis.title.y = element_blank(),
		axis.ticks = element_blank(),
		axis.text.x = element_text(size = 7, angle = 90, hjust = 1, vjust = 1)
	)

@@

### Prior predictions (before seeing the data)

```{r gaze_time_prior, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants %>% 
	filter(valid_participant) %>% 
	count(lp, vocab_size_total_center)

n <- expand_grid(
	lp = c("Monolingual", "Bilingual"),
	vocab_size_l1_center = c(-1, 1),
	trial_type = unique(gaze$trial_type),
	time_bin_center = seq(min(gaze$time_bin_center), max(gaze$time_bin_center), 0.1)
)

m <- epred_draws(fit_l1_prior, newdata = n, ndraws = 50, re_formula = NA) %>% 
	mutate(
		.value = logit_to_prob(.epred),
		vocab_size_l1_center = ifelse(
			vocab_size_l1_center==-1, 
			"Low vocabulary size (-1 SD)",
			"High vocabulary size (+1 SD)"
		)
	)

ggplot(m, aes(time_bin_center, .value)) +
	facet_grid(fct_rev(lp)~vocab_size_l1_center) +
	geom_hline(yintercept = 0.5, colour = "black") +
	geom_line(
		aes(group = interaction(vocab_size_l1_center, trial_type, lp, .draw),
			colour = trial_type),
		alpha = 0.5, size = 0.65
	) +

	labs(x = "Time bin (100 ms)", y = "Expected posterior mean PTLT", colour = "Trial type",
		 fill = "Trial type", shape = "Trial type", linetype = "Trial type") +
	scale_color_futurama() +
	scale_x_continuous(
		breaks = min(gaze$time_bin_center):max(gaze$time_bin_center), 
		labels = 1:20
	) +
	scale_y_continuous(
		limits = c(0, 1), 
		labels = percent
	) + 
	theme_minimal() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(size = 7),
		panel.grid.major.x = element_blank(),
		panel.grid.minor.x = element_blank(),
		panel.background = element_rect(fill = "white", colour = NA),
		plot.background = element_rect(fill = "white", colour = NA)
	)

@@

sample_size <- participants %>% 
	filter(valid_participant) %>% 
	count(lp, age_group, vocab_size_total_center)

@@

m %>% 
	ggplot() +
	aes(
		x = time_bin_center, 
		y = .value,
		colour = trial_type,
		fill = trial_type,
		linetype = trial_type,
		shape = trial_type
	) +
	facet_wrap(
		fct_rev(lp)~age_group,
		scales = "free",
		labeller = label_wrap_gen(multi_line = FALSE)
	) +
	geom_hline(
		yintercept = 0.5,
		colour = "black"
	) +
	# geom_line(
	# 	aes(group = interaction(trial_type, lp, .draw),
	# 		colour = trial_type),
	# 	alpha = 0.5, size = 0.65
	# ) +
	stat_summary(
		fun.data = mean_qi,
		geom = "ribbon",
		colour = NA,
		alpha = 0.25
	) +
	stat_summary(
		fun = mean,
		geom = "line",
		size = 0.75
	) +
	geom_text(
		data = sample_size,
		aes(
			x = min(gaze$time_bin_center),
			y = 1,
			label = paste0("N = ", n)
		),
		colour = "black",
		hjust = 0,
		vjust = 1,
		inherit.aes = FALSE
	) +
	geom_point(
		data = observed,
		size = 1.5
	) +
	labs(
		x = "Time from target-distractor onset (ms)", 
		y = "Posterior mean PTLT",
		colour = "Trial type",
		fill = "Trial type", 
		shape = "Trial type",
		linetype = "Trial type"
	) +
	scale_color_d3() +
	scale_fill_d3() +
	scale_x_continuous(
		breaks = seq(
			min(gaze$time_bin_center),
			max(gaze$time_bin_center),
			len = 7
		),
		labels = format(
			100*(seq(3, 18, 3)), 
			big.mark = ",", trim = TRUE
		)
	) +
	scale_y_continuous(
		limits = c(0, 1),
		labels = percent
	) + 
	theme_custom() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(face = "plain"),
		axis.text.y = element_text(face = "plain"),
		panel.grid.major.x = element_blank(),
		panel.grid.minor.x = element_blank(),
		panel.background = element_rect(
			fill = NA, 
			colour = NA
		),
		plot.background = element_rect(
			fill = "white",
			colour = NA
		)
	)

@@

nd <- expand_grid(
	lp = c("Monolingual", "Bilingual"),
	trial_type = unique(gaze$trial_type),
	age_group = unique(gaze$age_group),
	time_bin_center = seq(min(gaze$time_bin_center), max(gaze$time_bin_center), 0.1)
)

m %>% 
	ggplot() +
	aes(
		x = time_bin_center, 
		y = .value,
		colour = trial_type,
		fill = trial_type,
		linetype = trial_type,
		shape = trial_type
	) +
	facet_grid(lp~age_group) +
	geom_hline(
		yintercept = 0.5,
		colour = "black"
	) +
	geom_line(
		data = observed
	) +
	geom_point(
		data = observed,
		size = 3
	) +
	geom_text(
		data = sample_size,
		aes(
			x = min(gaze$time_bin_center),
			y = 1,
			label = paste0("N = ", n)
		),
		colour = "black",
		hjust = 0,
		vjust = 1,
		inherit.aes = FALSE
	) +
	labs(
		x = "Time bin (100 ms)", 
		y = "Expected posterior mean PTLT",
		colour = "Trial type",
		fill = "Trial type", 
		shape = "Trial type",
		linetype = "Trial type"
	) +
	scale_color_d3() +
	scale_fill_d3() +
	scale_x_continuous(
		breaks = seq(
			min(gaze$time_bin_center),
			max(gaze$time_bin_center),
			len = 5
		),
		labels = format(
			100*(seq(0, 20, 5)), 
			big.mark = ","
		)
	) +
	scale_y_continuous(
		limits = c(0, 1),
		labels = percent
	) + 
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid.major.x = element_blank(),
		panel.grid.minor.x = element_blank(),
		panel.background = element_rect(fill = "white", colour = NA),
		plot.background = element_rect(fill = "white", colour = NA)
	)

ggsave(here("img", "predictions_observed.png"))

>>>>

	# cubic terms ----
	"b_Itime_bin_centerE3:trial_typerelated_unrelated:lpLPMonvs.Bil:age_group21_25" = 
		"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Age (21 vs. 25 mo)",

	"b_Itime_bin_centerE3:trial_typerelated_unrelated:lpLPMonvs.Bil:age_group25_30" = 
		"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Age (25 vs. 30 mo)",

	"b_Itime_bin_centerE3:trial_typecognate_noncognate:lpLPMonvs.Bil:age_group21_25" = 
		"Trial type (C vs. NC) \u00d7 Group \u00d7 Age (21 vs. 25 mo)",

	"b_Itime_bin_centerE3:trial_typecognate_noncognate:lpLPMonvs.Bil:age_group25_30" = 
		"Trial type (C vs. NC) \u00d7 Group \u00d7 Age (25 vs. 30 mo)",

	"b_Itime_bin_centerE3:trial_typecognate_noncognate:lpLPMonvs.Bil" = 
		"Trial type (C vs. NC) \u00d7 Group",

@@

	"b_Itime_bin_centerE3:trial_typerelated_unrelated:age_group21_25" = 
		"Trial type (U vs. C+NC) \u00d7 Age (21 vs. 25 mo)",

	"b_Itime_bin_centerE3:trial_typerelated_unrelated:age_group25_30" = 
		"Trial type (U vs. C+NC) \u00d7 Age (25 vs. 30 mo)",

	"b_Itime_bin_centerE3:trial_typecognate_noncognate:age_group21_25" = 
		"Trial type (C vs. NC) \u00d7 Age (21 vs. 25 mo)",

	"b_Itime_bin_centerE3:trial_typecognate_noncognate:age_group25_30" = 
		"Trial type (C vs. NC) \u00d7 Age (25 vs. 30 mo)",

	"b_Itime_bin_centerE3:lpLPMonvs.Bil:age_group21_25" =
		"Group (ML vs. BL) \u00d7 Age (21 vs. 25 mo)",

	"b_Itime_bin_centerE3:lpLPMonvs.Bil:age_group25_30" =
		"Group (ML vs. BL) \u00d7 Age (25 vs. 30 mo)",

@@

	"b_Itime_bin_centerE3:age_group21_25" = 
		"Age (21 vs. 25 mo)",

	"b_Itime_bin_centerE3:age_group25_30" = 
		"Age (25 vs. 30 mo)",

@@

	"b_Itime_bin_centerE3" = 
		"Intercept",

	# quadratic terms ----
	"b_Itime_bin_centerE2:trial_typerelated_unrelated:lpLPMonvs.Bil:age_group21_25" = 
		"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Age (21 vs. 25 mo)",

	"b_Itime_bin_centerE2:trial_typerelated_unrelated:lpLPMonvs.Bil:age_group25_30" = 
		"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Age (25 vs. 30 mo)",

	"b_Itime_bin_centerE2:trial_typecognate_noncognate:lpLPMonvs.Bil:age_group21_25" = 
		"Trial type (C vs. NC) \u00d7 Group \u00d7 Age (21 vs. 25 mo)",

	"b_Itime_bin_centerE2:trial_typecognate_noncognate:lpLPMonvs.Bil:age_group25_30" = 
		"Trial type (C vs. NC) \u00d7 Group \u00d7 Age (25 vs. 30 mo)",

	"b_Itime_bin_centerE2:trial_typecognate_noncognate:lpLPMonvs.Bil" = 
		"Trial type (C vs. NC) \u00d7 Group",

@@

	"b_Itime_bin_centerE2:trial_typerelated_unrelated:age_group21_25" = 
		"Trial type (U vs. C+NC) \u00d7 Age (21 vs. 25 mo)",

	"b_Itime_bin_centerE2:trial_typerelated_unrelated:age_group25_30" = 
		"Trial type (U vs. C+NC) \u00d7 Age (25 vs. 30 mo)",

	"b_Itime_bin_centerE2:trial_typecognate_noncognate:age_group21_25" = 
		"Trial type (C vs. NC) \u00d7 Age (21 vs. 25 mo)",

	"b_Itime_bin_centerE2:trial_typecognate_noncognate:age_group25_30" = 
		"Trial type (C vs. NC) \u00d7 Age (25 vs. 30 mo)",

	"b_Itime_bin_centerE2:lpLPMonvs.Bil:age_group21_25" =
		"Group (ML vs. BL) \u00d7 Age (21 vs. 25 mo)",

	"b_Itime_bin_centerE2:lpLPMonvs.Bil:age_group25_30" =
		"Group (ML vs. BL) \u00d7 Age (25 vs. 30 mo)",

@@

	"b_Itime_bin_centerE2:age_group21_25" = 
		"Age (21 vs. 25 mo)",

	"b_Itime_bin_centerE2:age_group25_30" = 
		"Age (25 vs. 30 mo)",

@@

	"b_Itime_bin_centerE2" = 
		"Intercept",

	# linear terms ----
	"b_time_bin_center:trial_typerelated_unrelated:lpLPMonvs.Bil:age_group21_25" = 
		"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Age (21 vs. 25 mo)",

	"b_time_bin_center:trial_typerelated_unrelated:lpLPMonvs.Bil:age_group25_30" = 
		"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Age (25 vs. 30 mo)",

	"b_time_bin_center:trial_typecognate_noncognate:lpLPMonvs.Bil:age_group21_25" = 
		"Trial type (C vs. NC) \u00d7 Group \u00d7 Age (21 vs. 25 mo)",

	"b_time_bin_center:trial_typecognate_noncognate:lpLPMonvs.Bil:age_group25_30" = 
		"Trial type (C vs. NC) \u00d7 Group \u00d7 Age (25 vs. 30 mo)",

	"b_time_bin_center:trial_typecognate_noncognate:lpLPMonvs.Bil" = 
		"Trial type (C vs. NC) \u00d7 Group",

@@

	"b_time_bin_center:trial_typerelated_unrelated:age_group21_25" = 
		"Trial type (U vs. C+NC) \u00d7 Age (21 vs. 25 mo)",

	"b_time_bin_center:trial_typerelated_unrelated:age_group25_30" = 
		"Trial type (U vs. C+NC) \u00d7 Age (25 vs. 30 mo)",

	"b_time_bin_center:trial_typecognate_noncognate:age_group21_25" = 
		"Trial type (C vs. NC) \u00d7 Age (21 vs. 25 mo)",

	"b_time_bin_center:trial_typecognate_noncognate:age_group25_30" = 
		"Trial type (C vs. NC) \u00d7 Age (25 vs. 30 mo)",

	"b_time_bin_center:lpLPMonvs.Bil:age_group21_25" =
		"Group (ML vs. BL) \u00d7 Age (21 vs. 25 mo)",

	"b_time_bin_center:lpLPMonvs.Bil:age_group25_30" =
		"Group (ML vs. BL) \u00d7 Age (25 vs. 30 mo)",

@@

	"b_time_bin_center:age_group21_25" = 
		"Age (21 vs. 25 mo)",

	"b_time_bin_center:age_group25_30" = 
		"Age (25 vs. 30 mo)",

@@

	"b_time_bin_center" = 
		"Intercept",

	# marginal terms ----
	"b_trial_typerelated_unrelated:lpLPMonvs.Bil:age_group21_25" = 
		"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Age (21 vs. 25 mo)",

	"b_trial_typerelated_unrelated:lpLPMonvs.Bil:age_group25_30" = 
		"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Age (25 vs. 30 mo)",

	"b_trial_typecognate_noncognate:lpLPMonvs.Bil:age_group21_25" = 
		"Trial type (C vs. NC) \u00d7 Group \u00d7 Age (21 vs. 25 mo)",

	"b_trial_typecognate_noncognate:lpLPMonvs.Bil:age_group25_30" = 
		"Trial type (C vs. NC) \u00d7 Group \u00d7 Age (25 vs. 30 mo)",

	"b_trial_typecognate_noncognate:lpLPMonvs.Bil" = 
		"Trial type (C vs. NC) \u00d7 Group",

@@

	"b_trial_typerelated_unrelated:age_group21_25" = 
		"Trial type (U vs. C+NC) \u00d7 Age (21 vs. 25 mo)",

	"b_trial_typerelated_unrelated:age_group25_30" = 
		"Trial type (U vs. C+NC) \u00d7 Age (25 vs. 30 mo)",

	"b_trial_typecognate_noncognate:age_group21_25" = 
		"Trial type (C vs. NC) \u00d7 Age (21 vs. 25 mo)",

	"b_trial_typecognate_noncognate:age_group25_30" = 
		"Trial type (C vs. NC) \u00d7 Age (25 vs. 30 mo)",

	"b_lpLPMonvs.Bil:age_group21_25" =
		"Group (ML vs. BL) \u00d7 Age (21 vs. 25 mo)",

	"b_lpLPMonvs.Bil:age_group25_30" =
		"Group (ML vs. BL) \u00d7 Age (25 vs. 30 mo)",

@@

	"b_age_group21_25" = 
		"Age (21 vs. 25 mo)",

	"b_age_group25_30" = 
		"Age (25 vs. 30 mo)",

@@

	# sigma
	"sigma" = "Standard deviation"
)

# cubic terms ----
levels <- c(
	"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Age (21 vs. 25 mo)",
	"Trial type (U vs. C+NC) \u00d7 Group \u00d7 Age (25 vs. 30 mo)",
	"Trial type (C vs. NC) \u00d7 Group \u00d7 Age (21 vs. 25 mo)",
	"Trial type (C vs. NC) \u00d7 Group \u00d7 Age (25 vs. 30 mo)",
	"Trial type (C vs. NC) \u00d7 Group",
	"Trial type (U vs. C+NC) \u00d7 Group",
	"Trial type (U vs. C+NC) \u00d7 Age (21 vs. 25 mo)",
	"Trial type (U vs. C+NC) \u00d7 Age (25 vs. 30 mo)",
	"Trial type (C vs. NC) \u00d7 Age (21 vs. 25 mo)",
	"Trial type (C vs. NC) \u00d7 Age (25 vs. 30 mo)",
	"Group (ML vs. BL) \u00d7 Age (21 vs. 25 mo)",
	"Group (ML vs. BL) \u00d7 Age (25 vs. 30 mo)",
	"Group (ML vs. BL)",
	"Age (21 vs. 25 mo)",
	"Age (25 vs. 30 mo)",
	"Trial type (C vs. NC)",
	"Trial type (U vs. C+NC)",
	"Standard deviation",
	"Intercept"
)

draws <- gather_draws(
	fit_3, 
	`b_.*`, 
	`sigma`,
	regex = TRUE
) %>% 
	mutate(
		.variable_name = str_replace_all(.variable, str_repl) %>% 
			factor(levels = levels),
		type = case_when(
			str_detect(.variable, "Itime_bin_centerE2") ~ "Quadratic time",
			str_detect(.variable, "Itime_bin_centerE3") ~ "Cubic time",
			str_detect(.variable, "time_bin_center") & 
				str_detect(.variable, "E2|E3", negate = TRUE) ~ "Linear time",
			str_detect(.variable, "sigma") ~ "Distributional",
			.variable=="b_Intercept" ~ "Distributional",
			TRUE ~ "Main effects",
		) %>% 
			factor(
				levels = c(
					"Main effects", 
					"Linear time", 
					"Quadratic time", 
					"Cubic time",
					"Distributional"
				), 
				ordered = TRUE
			),
		.value = ifelse(
			(.variable %in% c("sigma", "b_Intercept")) & (type=="Main effects"),
			inv_logit(.value),
			.value/4
		),
	)

coefs_tab <- draws %>% 
	group_by(.variable_name, type) %>% 
	mean_qi(
		.exclude = c(
			".chain",
			".iteration",
			".variable",
			".draw",
			".row",
			".variable_name", 
			"type"
		)
	) %>%  
	mutate(.variable_name = factor(.variable_name, levels = rev(levels))) %>% 
	arrange(type, .variable_name) %>% 
	select(type, .variable_name, .value, .lower, .upper) %>% 
	gt(
		rowname_col = ".variable", 
		groupname_col = "type"
	)  %>% 
	row_group_order(
		groups = c(
			"Main effects", 
			"Linear time", 
			"Quadratic time", 
			"Cubic time",
			"Distributional"
		)
	) %>% 
	fmt_percent(3) %>%
	fmt_number(4:5, scale_by = 100) %>% 
	cols_merge(
		c(".lower", ".upper"), 
		pattern = "[{1}, {2}]"
	) %>% 
	cols_label(
		.variable_name = md("**Predictor**"),
		.value = md("**Mean**"),
		.lower = md("**95% CrI**")
	) %>% 
	tab_style(
		cell_text(weight = "bold", style = "italic"),
		cells_row_groups()
	) %>% 
	tab_style(
		cell_text(align = "left"),
		cells_body()
	) %>% 
	tab_style(
		style = cell_fill(color = pal_d3()(2)[1]),
		locations = cells_body(
			columns = everything(),
			rows = .lower > 0
		)
	) %>% 
	tab_style(
		style = cell_fill(color = pal_d3()(2)[2]),
		locations = cells_body(
			columns = everything(),
			rows = .upper < 0
		)
	)

gtsave(coefs_tab, here("img", "coefs_tab.png"))
as_raw_html(coefs_tab)
```

```{r main_effects_plot, echo=FALSE, message=FALSE, warning=FALSE, fig.height=10, fig.width=15}

draws %>% 
	filter(!(type %in% c("Standard deviation", "Intercept"))) %>% 
	group_by(type, .variable, .variable_name) %>% 
	summarise(
		.lower = quantile(.value, 0.025),
		.upper = quantile(.value, 0.975),
		.value = mean(.value),
		.groups = "drop"
	) %>% 
	mutate(
		excludes_zero = (.lower > 0) | (.upper < 0),
		excludes_zero = ifelse(excludes_zero, "Yes", "No") %>% 
			factor(levels = c("Yes", "No"))
	) %>% 
	ggplot() +
	aes(
		x = .value, 
		y = .variable_name,
		xmin = .lower,
		xmax = .upper,
		colour = excludes_zero
	) +
	facet_wrap(
		~type, 
		nrow = 1, 
		scales = "free_x"
	) +
	geom_vline(
		xintercept = 0,
		colour = "black", 
		linetype = "dashed"
	) +
	geom_pointinterval(
		size = 5,
		point_size = 3
	) +
	labs(
		x = "Value", 
		y = "Variable", 
		fill = "CrI", 
		alpha = "CrI",
		title = "Main effects",
		subtitle = "Mean and 95% credible interval of posterior distribution",
		colour = "Interval excludes zero?"
	) +
	scale_color_manual(values = rev(pal_d3()(2))) +
	scale_x_continuous(
		labels = percent
	) +
	theme(
		legend.position = "top",
		axis.title.y = element_blank(),
		axis.text.y = element_text(hjust = 1),
		panel.border = element_rect(colour = "black", fill = NA)
	)

ggsave(here("img", "coefficients.png"), height = 10, width = 16)
```

@@

@@

@@

m %>% 
	ggplot() +
	aes(
		x = time_bin_center, 
		y = .value,
		colour = trial_type,
		fill = trial_type,
		linetype = trial_type,
		shape = trial_type
	) +
	facet_wrap(
		fct_rev(lp)~age_group,
		scales = "free",
		labeller = label_wrap_gen(multi_line = FALSE)
	) +
	geom_hline(
		yintercept = 0.5,
		colour = "black"
	) +
	# geom_line(
	# 	aes(group = interaction(trial_type, lp, .draw),
	# 		colour = trial_type),
	# 	alpha = 0.5, size = 0.65
	# ) +
	stat_summary(
		fun.data = mean_qi,
		geom = "ribbon",
		colour = NA,
		alpha = 0.25
	) +
	stat_summary(
		fun = mean,
		geom = "line",
		size = 0.75
	) +
	geom_text(
		data = sample_size,
		aes(
			x = min(gaze$time_bin_center),
			y = 1,
			label = paste0("N = ", n)
		),
		colour = "black",
		hjust = 0,
		vjust = 1,
		inherit.aes = FALSE
	) +
	geom_point(
		data = observed,
		size = 1.5
	) +
	labs(
		x = "Time from target-distractor onset (ms)", 
		y = "Posterior mean PTLT",
		colour = "Trial type",
		fill = "Trial type", 
		shape = "Trial type",
		linetype = "Trial type"
	) +
	scale_color_d3() +
	scale_fill_d3() +
	scale_x_continuous(
		breaks = seq(
			min(gaze$time_bin_center),
			max(gaze$time_bin_center),
			len = 6
		),
		labels = format(
			100*(seq(3, 18, 3)), 
			big.mark = ",", trim = TRUE
		)
	) +
	scale_y_continuous(
		limits = c(0, 1),
		labels = percent
	) + 
	theme_custom() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(face = "plain"),
		axis.text.y = element_text(face = "plain"),
		panel.grid.major.x = element_blank(),
		panel.grid.minor.x = element_blank(),
		panel.background = element_rect(
			fill = NA, 
			colour = NA
		),
		plot.background = element_rect(
			fill = "white",
			colour = NA
		)
	)

@@

observed %>% 
	ggplot() +
	aes(
		x = time_bin_center, 
		y = .value,
		colour = trial_type,
		fill = trial_type,
		linetype = trial_type,
		shape = trial_type
	) +
	facet_wrap(
		fct_rev(lp)~age_group,
		scales = "free",
		labeller = label_wrap_gen(multi_line = FALSE)
	) +
	geom_hline(
		yintercept = 0.5,
		colour = "black"
	) +
	geom_line() +
	geom_point(
		size = 2
	) +
	geom_text(
		data = sample_size,
		aes(
			x = min(gaze$time_bin_center),
			y = 1,
			label = paste0("N = ", n)
		),
		colour = "black",
		hjust = 0,
		vjust = 1,
		inherit.aes = FALSE
	) +
	labs(
		x = "Time from target-distractor onset (ms)", 
		y = "Observed PTLT",
		colour = "Trial type",
		fill = "Trial type", 
		shape = "Trial type",
		linetype = "Trial type"
	) +
	scale_color_d3() +
	scale_fill_d3() +
	scale_x_continuous(
		breaks = seq(
			min(gaze$time_bin_center),
			max(gaze$time_bin_center),
			len = 6
		),
		labels = format(
			100*(seq(3, 18, 3)), 
			big.mark = ",", trim = TRUE
		)
	) +
	scale_y_continuous(
		limits = c(0, 1),
		labels = percent
	) + 
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(face = "plain"),
		axis.text.y = element_text(face = "plain"),
		panel.grid.major.x = element_blank(),
		panel.grid.minor.x = element_blank(),
		panel.background = element_rect(
			fill = NA, 
			colour = NA
		),
		plot.background = element_rect(
			fill = "white",
			colour = NA
		)
	)

ggsave(
	here("img", "predictions_observed.png"),
	dpi = 2000,
	height = 7,
	width = 12
)
```

```{r coefs-aggregated, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

str_repl_agg <- c(
